\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-14 paper/paper.tex
Revise abstract

% For submission make this a noop
\newcommand{\note}[2]{\textit{[#1: #2]}}
\newcommand{\nikita}[1]{\note{nikita}{#1}}

% to be able to draw some self-contained figs
\usepackage{tikz}
%\usepackage{parskip}
\usepackage{amsmath}
\usepackage{wasysym}
%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
\setlength\parskip{1pt}
\usepackage{graphicx} % http://ctan.org/pkg/graphicx
\usepackage{booktabs} % http://ctan.org/pkg/booktabs
\usepackage{xparse}   % http://ctan.org/pkg/xparse%don't print date
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
\include{figures}
\usepackage{subcaption}
\usepackage{cleveref}

@@

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
Refraction Networking (formerly ``Decoy Routing'') has emrged as a useful tool in circumventing
        Internet censorship. By placing proxies in cooperating Internet Service
        Providers (ISPs) and using connections to existing reachable
        ``decoy'' sites for transport, censors cannot easily block access to
        such proxies without also blocking legitimate sites.

However, existing deployed Refraction Networking schemes such as TapDance suffer
from several problems, including a limited number of decoy sites in realistic
deployments, and an unfavorable tradeoff between performance and observability
by the censor. These problems limit where such proxies can be deloyed, hamper
their effectiveness, and may ultimately make them possible for censors to block.

In this paper, we present Dark Decoys, a deployable Refraction Networking scheme that
overcomes the limits on decoys and performance. Dark Decoys leverages the (primarily) unused address
space that is reachable through the deploying ISP. Rather than rely on existing
sites as reachable decoy sites that must be involved in each proxy connection,
Dark Decoys create seemingly legitimate hosts at new IP addresses. These
invented hosts are indistinguishable from normal hosts to the censor, but can
be used by clients as one-time proxies.

We implement our scheme ... and it's just the bee's knees. TODO

@@

%-------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{biblio}

>>>>

% For submission make this a noop

% to be able to draw some self-contained figs
\usepackage{tikz}
%\usepackage{parskip}
\usepackage{amsmath}
\usepackage{wasysym}
%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
\setlength\parskip{1pt}
\usepackage{graphicx} % http://ctan.org/pkg/graphicx
\usepackage{booktabs} % http://ctan.org/pkg/booktabs
\usepackage{xparse}   % http://ctan.org/pkg/xparse%don't print date
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
\include{figures}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{microtype}

\usepackage{xspace}
\usepackage{soul}
\newcommand{\note}[2]{\hl{[\textbf{#1:} #2]}\xspace}
\newcommand{\nikita}[1]{\note{nikita}{#1}}

% Slight JAH fix to stop URLs from breaking after ``http:''
\def\UrlBreaks{\do-\do\.\do\@\do\\\do\!\do\_\do\|\do\;\do\>\do\]%
 \do\)\do\,\do\?\do\'\do+\do\=\do\#}
\def\UrlBigBreaks{\do\:\do\/}%
\urlstyle{rm}

@@

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
Refraction Networking (formerly known as ``Decoy Routing'') has
emerged as a promising next-generation approach for circumventing
Internet censorship. Rather than trying to hide individual
circumvention proxy servers from censors, proxy functionality is
implemented in the core of the network, at cooperating ISPs in
friendly countries.  Any connection that traverses these ISPs could be
a conduit for the free flow of information, so censors cannot easily
block access without also blocking many legitimate sites.  While one
Refraction scheme, TapDance, has recently been deployed at ISP-scale,
it suffers from several problems: a limited number of ``decoy'' sites
in realistic deployments, high technical complexity, and undesirable
tradeoffs between performance and observability by the censor. These
problems may impede broader deployment and ultimately allow censors to
block such techniques.

We present Dark Decoys, an improved Refraction Networking approach
that overcomes these limitations by leveraging unused address space at
deploying ISPs. Instead of using real websites as the decoy destinations
for proxy connections, our scheme creates seemingly legitimate hosts
on demand, at IP addresses where no web server exists.
These phantom hosts are difficult for a censor to distinguish from
ones, but can be used by clients as proxies.  We define the
Dark Decoys protocol, analyze its security, and evaluate a
prototype on IPv4 and IPv6 networks.
Our results suggest that Dark Decoys can be as difficult to block
as TapDance, is simpler to maintain and deploy,
and offers substantially better network performance.

@@

%-------------------------------------------------------------------------------

\bibliographystyle{plain}
\small
\bibliography{biblio}
